Human capital mediates natural selection in contemporary humans

### 2022-03-28 why-natural-selection.Rmd
Talk about RLRS in mediation analysis

We run a standard mediation analysis in the framework of @baron1986moderator.
For each polygenic score where the bivariate correlation with fertility is 
significant at $p$ < 0.05/33, we estimate 
\begin{align}
N_i & = \alpha + \beta PGS_i + \gamma EA_i + X_i\mu + \varepsilon_i \\
EA_i & = \delta + \zeta PGS_i + X_i\mu + \eta_i
\end{align}
where $N_i$ is fertility, $PGS_i$ is the polygenic score, $EA_i$ is educational
attainment (age of leaving fulltime education), and $X_i$ is a vector of
controls. The total effect of $PGS$ on number of children is $\beta + \gamma
\zeta$. The "indirect effect" mediated by $EA$ is $\gamma \zeta$. The standard
error of the indirect effect can be calculated as

>>>>

We run a standard mediation analysis in the framework of @baron1986moderator.
For each polygenic score where the bivariate correlation with RLRS is 
significant at $p$ < 0.05/33, we estimate 
\begin{align}
RLRS_i & = \alpha + \beta PGS_i + \gamma EA_i + X_i\mu + \varepsilon_i \\
EA_i & = \delta + \zeta PGS_i + X_i\mu + \eta_i
\end{align}
where $RLRS_i$ is fertility, $PGS_i$ is the polygenic score, $EA_i$ is educational
attainment (age of leaving fulltime education), and $X_i$ is a vector of
controls. The total effect of $PGS$ on number of children is $\beta + \gamma
\zeta$. The "indirect effect" mediated by $EA$ is $\gamma \zeta$. The standard
error of the indirect effect can be calculated as
